---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
p {
font-family: 'Lucida Console';
}

h4 {
font-family: 'Lucida Console';
}
```

## How has everyones mood been lately?


```{r}
library(tidyverse)

#The link to my spreadsheet detailing my collection of data from the form
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ9gAgH-hQJyxJVLKnIGTqyKzeH8vguUh34yd3g5fnoiL1f6-zL6Orf8JO6KfDNIF1JPQYvKm467TqS/pub?output=csv")


#Renaming the columns of the data 
latest_data <- logged_data %>%
  rename(response_time = 1,
    mood_rating = 2,
    current_mood = 3,
    mood_improvement = 4)


#Summary value one, where I find the highest mood rating in the data
summary_one <- latest_data %>% 
  select(mood_rating) %>% 
  max()


#Summary value two, where I find the sum of all the mood ratings 
summary_two <- latest_data %>% 
  select(mood_rating) %>% 
  sum()


#Bar chart showcasing the current moods among the data to observe which mood is the most apparent
graph_one <- latest_data %>% 
  ggplot() +
    geom_bar(aes(x = current_mood, fill = current_mood)) +
  labs(title = "Mood Tracker",
       subtitle = "Comparing how different peoples moods are as of current time of filling out the Google form",
       caption = "Source: Mood Tracker form",
       x = "Moods",
       y = "Number of responses")


#Bar chart showcasing the current moods of respondents with various mood improving suggestions that they have for themselves
graph_two <- latest_data %>% 
  ggplot() +
    geom_bar(aes(y = mood_improvement, fill = current_mood)) +
  labs(title = "Improving Current Moods",
       subtitle = "Viewing the numerous mood improvement suggestions that correlate to respondents current mood",
       caption = "Source: Mood Tracker form",
       x = "Amount of different suggestions",
       y = "Various improvement suggestions")

```

### Summary Values

<h4> Summary Value #1 </h4>
The highest recorded mood scale from 1-10 was `r summary_one`.


7/10 is the max value in terms of being in a good mood recorded within the data.

<h4> Summary Value #2 </h4>

The total of all the mood scale ratings from 1-10 was `r summary_two`.


This shows that the mood scale ratings are relatively low for most responses.

### Bar Charts

<h4> Graph One: Most Common Moods </h4>

``` {r}
graph_one <- latest_data %>% 
  ggplot() +
    geom_bar(aes(x = current_mood, fill = current_mood)) +
  labs(title = "Mood Tracker",
       subtitle = "Comparing how different peoples moods are as of current time of filling out the Google form",
       caption = "Source: Mood Tracker form",
       x = "Moods",
       y = "Number of responses")

print(graph_one)
```

This bar chart shows that the most common mood among respondents is *Stressed*.


<h4> Graph Two: Self Mood Improvement Suggestions based on Current Moods recorded </h4>

``` {r}
graph_two <- latest_data %>% 
  ggplot() +
    geom_bar(aes(y = mood_improvement, fill = current_mood)) +
  labs(title = "Improving Current Moods",
       subtitle = "Viewing the numerous mood improvement suggestions that correlate to respondents current mood",
       caption = "Source: Mood Tracker form",
       x = "Amount of different suggestions",
       y = "Various improvement suggestions")

print(graph_two)
```

This bar chart shows a common theme of stress eating and finishing assignments as a mood improving method especially if the current mood is **Stressed**.
